Weather Data Integration and Assimilation System\\

### 2020-02-15 summary/sec_1-conclusions.tex
Address all the comments. Next proofreading

To enhance the accuracy of the weather prediction, it is essential to provide reliable and timely weather data for \acrshort{nwm}. Even though there are many data integration systems, most of them are proprietary or close sourced. Which means for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized. \hl{Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. Also most of existing systems are not up to date with the cloud computing technologies, or bias to some research community.}

/dbc{Look some of the changes in abstract and revise this para. However, don't repeat the same from abstract.}

>>>>

To enhance the accuracy of the weather prediction, it is essential to provide reliable and timely weather data for \acrshort{nwm}. Even though there are many weather data integration systems, most of them are proprietary or close sourced. Which means for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized. %\hl{Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. Also most of existing systems are not up to date with the cloud computing technologies, or bias to some research community.}
\hl{Also most of existing systems are based on basic client-server architectures or monolithic distributed system architectures which are popular or available at the time of developing those systems. Because of this, those are unable to get the advantage of modern computational models such as containerized applications and using the could computing in order to gain benefits of scalability, high availability and low-cost operations.}

\dbc{Look some of the changes in abstract and revise this para. However, don't repeat the same from abstract.}
\gkc{UPDATED}
